eda

### 2022-08-28 hw1-1/eda_27082022.Rmd
added EDA
added 2.1 part 1,2

---
title: "R Notebook"
output: html_notebook
---

@@

4.  Correlation Heat Map
```{r}
cormat <- round(cor(org_cc_data),2)
cormat[upper.tri(cormat)] <- NA
melted_cormat <- melt(cormat)
# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2,
                                   fill=value)) +
geom_tile() +
geom_text(aes(Var1, Var2, label = value),
          color = "white", size = 3)
```
If |cor| >0.3 ==> Significant (Let)
R1: A8,A9,A10,A11
A11: A8,A9,A10
A10: A9
A9: A8
A8: A2

>>>>

---
title: "eda"
output: github_document
---

@@

4.  Correlation Heat Map
```{r}
cormat <- round(cor(org_cc_data),2)
cormat[upper.tri(cormat)] <- NA
melted_cormat <- melt(cormat)
# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2,
                                   fill=value)) +
geom_tile() +
geom_text(aes(Var1, Var2, label = value),
          color = "white", size = 3)
```
If |cor| > 0.3 ==> Significant (Let)
R1: A8,A9,A10,A11
A11: A8,A9,A10
A10: A9
A9: A8
A8: A2
